---
title: "Aaron Gullickson's CV"
author: Aaron Gullickson
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(magrittr) # For the pipe
source("cv_printing_functions.r")

# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1scjvE65qm5YXS-JG4-CRPiLEqsz6p4y34WX6ipEct_w/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)

```


```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```


Aside
================================================================================

```{r}
# Build interactive network of positions colored by section
# and connected if they occurred in the same year
#datadrivencv::build_network_logo(CV$entries_data)
```


```{r}
if(params$pdf_mode){
  cat("[View this CV online with links](https://aarongullickson.netlify.app/cv/)")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://aarongullickson.netlify.app/cv/aarongull_cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------

```{r}
CV %>% print_contact_info()
```


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()`.



Main
================================================================================

Aaron Gullickson {#title}
--------------------------------------------------------------------------------

```{r}
# Note the special double pipe so we modify the CV object in place
CV %<>% print_text_block("intro") 
```


Employment {data-icon=suitcase}
--------------------------------------------------------------------------------



```{r}
CV %<>% print_section('employment')
```


Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('education_aside')
```
:::

```{r}
CV %<>% print_section('education')
```

Publications {data-icon=book data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('academic_articles')
```

Grants Awarded {data-icon=money-bill data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('grants_awarded')
```

Recent Invited Talks {data-icon=comment data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('invited_talks')
```

Recent Conference Presentations {data-icon=users data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('conference_talks')
```

Courses Taught {data-icon=chalkboard-teacher data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('courses_aside')
```
:::

```{r}
CV %<>% print_section('classes_taught')
```

Student Advising {data-icon=people-carry data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('students_advised')
```

Service, Departmental {data-icon=home data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('service_department')
```

Service, University {data-icon=home data-concise=true}
--------------------------------------------------------------------------------

```{r}
CV %<>% print_section('service_university')
```

Service, Professional {data-icon=home data-concise=true}
--------------------------------------------------------------------------------

::: aside
```{r}
CV %<>% print_text_block('service_aside')
```
:::


```{r}
CV %<>% print_section('service_professional')
```


```{r}
CV %<>% print_links()
```

